Hydra Battles and Cie

### 2021-05-17 doc/part-hydras.tex
small change in doc and comments

%\section{Introduction}

>>>>

\begin{remark}
Some notations (mainly names of fast-growing functions) of our development may differ slightly from the litterature. Although this fact does not affect our proofs, we are preparing a future 
version where the names $F\_alpha$, $f\_alpha$, $H\_alpha$, etc., are fully consistent with the cited articles. This change will be provisionally made in a branch \texttt{Hardy} (in reference to the Hardy hierarchy).
\end{remark}
%\section{Introduction}
